---
output:
  md_document:
    variant: markdown_github
---

# Purpose

Purpose of this work folder.

Ideally store a minimum working example data set in data folder.

Add binary files in bin, and closed R functions in code. Human Readable settings files (e.g. csv) should be placed in settings/


```{r}

#rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

```{r, eval=F}
fmxdat::make_project(Open = T)

 CHOSEN_LOCATION <- "C:/Users/Erik Schulte/ownCloud/Uni Göttingen/Stellenbosch University/Data Science Methods/26802325/"
fmxdat::make_project(FilePath = glue::glue("{CHOSEN_LOCATION}Solution/"), 
                    ProjNam = "___26802325")

Texevier::create_template_html(directory = glue::glue("{CHOSEN_LOCATION}Solution/"), template_name = "Q1")
Texevier::create_template_html(directory = glue::glue("{CHOSEN_LOCATION}Solution/"), template_name = "Q2")
Texevier::create_template_html(directory = glue::glue("{CHOSEN_LOCATION}Solution/"), template_name = "Q3")
Texevier::create_template(directory = glue::glue("{CHOSEN_LOCATION}Solution/"), template_name = "Q4")
```



# Question 1 Solution

```{r}
# Data loading:
    Loc <- "data/Prac2022/Covid/"
    cov_description <- read.csv(glue::glue("{Loc}covid_data_description.csv"))
    deaths_cause <- read.csv(glue::glue("{Loc}Deaths_by_cause.csv"))
    owid_data <- read.csv(glue::glue("{Loc}owid-covid-data.csv"))
    library(tidyverse)
library(ggplot2)
library(dplyr)
```


```{r, eval=F}
gg <- cases_per_region(continents,  xaxis_size = 5, xaxis_rows = 3)
gg
```
We can see that as of this week Africa had by far the fewest total cases compared to the other continents in the dataframe. Less than 15 Million COVID cases, where as Other regions like the US and Europe and Asia had more than 100 million cases or well above.  But obviously this has multiple reasons like different populations sizes and testing capacities.



```{r, eval=F}
ggg <- deaths_per_region(continents,  xaxis_size = 5, xaxis_rows = 3)
ggg
```
We can further see that this is also reflected in the deaths per region Africa is the only continent with less than 500,000 deaths related to COvid while all other continents had at least 1 Million so far. There is definetely a corrleation between cases and total deaths in the regions. 


```{r}
# summary(owid_data$female_smokers)
# summary(owid_data$aged_65_older)
```


First, of all we not that theere is very little data on ICU admissions and patients since the vast majority is NA's as the summary command shows.

```{r}
# <- owid_data[owid_data$iso_code %in% c("OWID_AFR", "OWID_ASI", "OWID_EUR", "OWID_NAM", "OWID_SAM"),] 
#no data available for OWID continents...
###add lagged ICU admissions
# summary(owid_data$icu_patients) 
# summary(owid_data$weekly_icu_admissions_per_million)
# unique(owid_data$icu_patients)

##regressions does not work
#regressions <- lm(formuala = lagged_ICU_patients ~ hospital_beds_per_thousand, data = owid_data)
```
# Question 2 Solution
```{r}
# Data loading:
library(readr)
library(lubridate)
london_weather <- read_csv("data/Prac2022/London/london_weather.csv", col_types = cols(date = col_date(format = "%Y%m%d")))

```


# Question 3 Solution


# Question 4 Solution